Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/comments/gz_hubble_data_cjl.tex
Smaller changes (via email) from CJL.

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH)
project.\footnote{This publication has been made possible by the participation
of more than 200,000~volunteers in the Galaxy Zoo project. Their contributions
are individually acknowledged at
\url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a
large effort to measure reliable, detailed morphologies of galaxies by using
crowdsourced visual classifications of color composite images. Images in GZH
were selected from various \textit{Hubble Space Telescope} Legacy programs
using the Advanced Camera for Surveys, with filters that probe the rest-frame
optical emission from galaxies out to $z\sim1$.  The bulk of the sample is
selected to have $m_{I814W}<23.5$ across AEGIS, COSMOS, GEMS, and 2-epoch
exposures in GOODS-N and GOODS-S. Full-depth 5-epoch images from the GOODS
fields are also included and have $m_{I814W}<26.8$. The median redshift of the
combined samples is $\langle z\rangle=0.9\pm0.6$, with a tail extending out to
$z\simeq4$. The GZH morphological data include measurements of both bulge- and
disk-dominated galaxies, details on spiral disk structure that relate to the
Hubble type, bar identification, and numerous measuremenst of clump
identification and geometry.  This paper also describes a new method for
calibrating morphological bias by using artificially-redshifted galaxy images
as a baseline. The GZH catalog contains both raw and calibrated morphological
vote fractions for $150,771$~galaxies, providing the largest dataset to date
suitable for large-scale studies of galaxy evolution out to $z\sim1$. 
\end{abstract}

@@

The morphology of galaxies encodes information on the orbital parameters and
assembly history of their contents, including gas, dust, stars, and the central
black hole. The morphology is also closely related to the local environment of
a galaxy, as interactions such as tides, shocks in cluster environments and
direct mergers can all influence a galaxy's internal structure.  For
$M^\star$~galaxies in the local Universe, this interplay between the physical
development of a galaxy and its external appearance typically manifests at the
most basic level as the difference between bulge-dominated systems with
no/little spiral structure (early-types) and disk-dominated,
rotationally-supported galaxies (late-types) frequently exhibiting spiral arms.
This dichotomy has been used to explore much of the astrophysics governing
galaxy formation and evolution, and has been shown to be closely linked with
other galactic properties such as stellar mass, halo mass, bolometric
luminosity, black hole activity, effective radius, and the relative ages of the
stellar populations.

The advent of larger telescopes in an increasing range of observing wavelengths
has revealed that the distribution and properties of galaxy morphology have
strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$
(roughly 6~Gyr after the Big Bang), many galaxies are still in the process of
assembling the baryonic and stellar mass required to reproduce the mature,
coherent structures seen at the present day. This growth occurs via a variety
of pathways, including accretion from large-scale galactic filaments onto halos
via streaming, mergers of individual halos, conversion of gas into stars via
gravitational collapse, etc. The accrual of baryons can be slowed or even
reversed via feedback from stellar winds, supernovae, and active black holes.
Each of these processes affects galaxy morphology in different ways, and so an
accurate measurement of morphological demographics as a function of redshift
provides an extremely powerful observational constraint on the physics involved
\citep[for recent reviews see][]{but13,con14}.

Theoretical predictions for the morphology of galaxies as a function of
redshift are primarily computed within the $\Lambda$CDM cosmological framework.
Full treatments model gravitational interactions between baryons and dark
matter, hydrodynamics of the gas, and baryonic physics related to star
formation and evolution. The most advanced simulations now span volumes up to
$\sim100$~Mpc$^3$ while simultaneously resolving the smaller ($<1$ kpc) scales
necessary to reproduce the influence of baryonic physics \citep{vog14a,sch15}.
Such simulations predict clustering of galaxies on large scales in a
hierarchical assembly model \citep{sil12}. The structure of individual galaxies
is affected by their merger history \citep{too72,ste02,hop10}, local
environment \citep[such as the morphology-density relation;][]{dre80}, initial
dark halo mass, secular evolution rate, and many other factors. Morphologies of
individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale
``clumpy'' structures, with few galaxies that are either smooth or well-ordered
spirals; asymmetric profiles with strong density contrasts dominate simulated
populations in the early Universe until at least $z\sim1$ \citep{bel12,gen14}.

Observational studies of galaxies at high-redshift also display a wide range of
morphological types, many of which are rare or absent at $z\sim0$. Although
spheroids and disks are present, they are typically much more compact than
those in the local Universe. There is also a significant population of more
irregular, massive galaxies, including mergers, tadpoles, chains,
double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In
contrast, while grand-design spirals have been observed as far back as $z=2.18$
\citep{law12}, their spatial density suggests that they are exceedingly rare,
with a very low fraction of undisturbed disks \citep{mor13}. Current
observational data thus strongly suggests that the classical Hubble
sequence/tuning fork \citep{hub36} is not a suitable framework for
characterizing high-redshift morphology.

Space-based observatories, particularly the \hubble{} (\hst), have been
responsible for the bulk of imaging studies of high-redshift galaxies.
Observations of fixed fields with very deep imaging
\citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric
sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also
providing the angular resolution to distinguish internal structure and
characterize the morphology. While these measurements are helped by the fact
that the angular diameter distance is relatively flat beyond $z>1$ in a flat
$\Lambda$CDM cosmology, the relevant angular scales are only of the order
$\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve
much of the structure for a Milky Way-sized galaxy (at least for distinguishing
a disk from a bulge), but will be limited for more compact structures. Since
the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$
\citep{mao98,law12a}, the compact sizes of high-redshift galaxies make detailed
morphologies a challenge even for \hst{} \citep{che12}. The public availability
of more than $10^5$~galaxies in archival imaging across various studies gives a
data sample with the potential for high statistical significance.

One of the major difficulties in studying the morphologies of galaxies lies in
the techniques used for measurement. Visual classification by experts has been
used for many decades \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}.
These methods have the advantage of using the significant processing power of
the human brain to identify patterns, but suffer from issues such as lack of
scaling to large surveys and potential issues with replicability and
calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12}
and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to
very large sample sizes, but do not always fully capture the relevant features,
especially for asymmetric galaxies that become increasingly common at high
redshifts. The Galaxy Zoo project \citep{lin08} utilizes crowdsourced visual
classifications to measure galaxies in color-composite images. The efforts of
more than $2\times10^5$~classifiers allow for multiple independent
classifications of each image which are combined and calibrated to give a
distribution of vote fractions proportional to the probability of a feature
being visible. While crowdsourced data require extensive calibration
\citep{bam09,wil13}, they have a proven reliability and have been used for a
wide variety of scientific studies
\citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the classifications collected from the Galaxy Zoo Hubble
(GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third
phase of Galaxy Zoo, following its initial results classifying
$\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and
Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed
classification scheme that included bars, spiral arms, and galactic bulges
\citep{wil13}. GZH used a similarly detailed classification scheme, but focused
for the first time on images of high-redshift galaxies taken with \hst. The
Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at
high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).

@@

This paper assumes the WMAP9 cosmological parameters of
$(\Omega_m,\Omega_\Lambda,h)=(0.282,0.718,0.697)$ \citep{hin13}.

@@

The GZH project contains images drawn from a number of different dedicated
surveys and sample selection criteria. The majority of the data (as implied by
the project name) were taken directly from \hst{} Legacy Surveys, all of which
primarily used imaging from the Advanced Camera for Surveys (ACS). Results from
the individual surveys have been combined into a single photometric and
morphological database, the Advanced Camera for Surveys General Catalog
\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
Table~\ref{tbl:gzh_numbers}.

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for
Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The
unfilled black curves show the filters for the Suprime Camera on \subaru, which
was used to create color gradients in the GZH COSMOS
images.\label{fig:filtercurves}}
\end{figure*}

The properties of the individual surveys are as follows:

\begin{itemize}

\item The All-Wavelength Extended Groth Strip International Survey
    \citep[AEGIS;][]{dav07} covers a strip centered at
    $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area
    of the sky was selected for a deep survey due to a combination of low
    extinction and low Galactic/zodiacal emission. The ACS images covered 63
    separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands
    for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and
    2100~seconds in F814W (\Iband). The final mosaic images were dithered
    to a resolution of 0.03~\arcsec/pixel. For extended objects, the
    limiting magnitude of sources was 26.23~(AB) in \Vband{} and 25.61 (AB) in
    \Iband.

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04}
    covered two separate fields in the northern and southern hemispheres: the Hubble
    Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m},
    \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South
    ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{}
    ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S,
    respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband),
    \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each
    epoch varied by band, from 1050--2100~seconds. The \Bband{} images were completed
    in a single epoch at the beginning of the survey, but the \Vband, \iband, and
    \zband{} images were taken in five separate epochs separated by 40--50~days
    each. Images were dithered to a pixel scale of 0.03~\arcsec/pixel and covered a
    total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The
    $5\sigma$ limiting magnitude for extended sources was 25.7 for \Vband{} and
    25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covered an area of
    $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m},
    \delta=+02^\circ12^\prime$. Its location near the celestial equator was
    designed to enable coverage by ground-based telescopes in both the Northern and
    Southern Hemispheres, in addition to space-based observatories. The ACS data
    for COSMOS consisted of 1~orbit per pointing with an exposure time of
    2028~seconds in \Iband; 590 total pointings were used to cover the entire
    field. The image resolution was dithered to 0.05~\arcsec/pixel. The 50\%
    completeness magnitude for a galaxy with a half-light radius of
    $0.50^{\prime\prime}$ in \Iband{} was 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDs
    \citep[GEMS;][]{rix04,cal08} survey was also centered on the Chandra Deep
    Field-South. The GEMS data covered $\sim800$~arcmin$^2$, completely surrounding
    the area covered by GOODS-S. Images from ACS in GEMS had 1 orbit per pointing
    for a total of 63~pointings. The exposure times were 2160 and 2286~seconds in
    \Vband{} and \zband{}, respectively. The image resolution had a pixel scale
    of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitude for source
    detection was 25.7 AB in \Vband{} and 24.2~AB in \zband.

\end{itemize}

@@

In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
113,166~images (Table~\ref{tbl:gzh_numbers}).

Single-epoch images from SDSS Stripe~82 were selected using the same criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
single-depth images and matched to a co-add source. This resulted in a total
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

@@

The images used for classification in GZH were color-composite JPEGs made from
multi-band data. These were created followed the method of \citet{lup04}, which
preserves colour information irrespective of intensity.  An asinh intensity
mapping was applied to enhance the appearance of faint features while avoiding
saturating galaxy centers. The relative scalings of the filter bands were
chosen while trying to reproduce the color appearance of the SDSS images in
previous iterations of Galaxy Zoo.

Many of the Legacy surveys described in Section~\ref{ssec:legacy_surveys}
provided images in only two filters. For these, the shorter-wavelength band was
mapped to the blue channel, the longer-wavelength band to the red channel, and
the green channel created by taking the arithmetic mean of the two. The bands
used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}.
Although four bands were available for the GOODS survey, only two bands were
used to create the original 2-epoch images, for consistency with AEGIS and
GEMS. The 2-epoch GOODS-N and GOODS-S images were created using different
filters --- this was a deliberate choice made so that the GEMS images could be
directly compared with the overlapping coverage of GOODS-S
(Figure~\ref{fig:filtercurves}).

Only 2-epoch GOODS images were included at the launch of GZH.  Deeper, 5-epoch 
GOODS images were added into GZH later (in March 2015). These images made
use of the full four-band data by using the arithmetic mean of \Bband{} and
\Vband{} in the blue channel, \Iband{} in the green channel, and \zband{} in
the red channel.

The COSMOS survey provided only \Iband{} HST imaging at the time of the GZH
launch.  These galaxies used ``pseudocolor'' images created by using
the ACS \Iband{} data as an illumination map and ground-based imaging from the
\subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide color
information (see \citealt{gri12} for further details). This resulted in images
with the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the
overall intensity, but color gradients at ground-based resolution, with seeing
between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.

Stripe~82 single-epoch images were taken directly from the DR7 SDSS Skyserver,
which combined $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the
RGB channels. The co-added Stripe~82 images were assembled from runs 106 and
206 in DR7 and processed into color composites in a corresponding manner.

In some cases, we found that attempting to emphasize faint features in the
images resulted in the sky noise taking the appearance of brightly colored
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the color images and a desaturation operation performed.
This masked procedure was effective in preserving the color balance for
galaxies, retaining the visibility of faint features, but reduced the color
contrast in the sky noise and greatly improved the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

@@

GZH also included a set of images designed to measure the effect of active
galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
can have bright, unresolved optical emission, AGN have the potential to mimic
or distort the identification of a bulge component. The presence of an AGN was
simulated by modeling the point spread function (PSF) of the telescope and then
inserting a bright source near the center of a real galaxy. For each image, the
simulated AGN was assigned one of three colors -- either blue, red, or flat
(white) as seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host.

>>>>

% Note: 250-word limit
We present the data release paper for the Galaxy Zoo: Hubble (GZH) project.\footnote{This publication has been made possible by the participation of more than 200,000 volunteers in the Galaxy Zoo project. Their contributions are individually acknowledged at \url{http://authors.galaxyzoo.org/authors.html}.} This is the third phase in a large effort to measure reliable morphologies of galaxies on detailed scales by using crowdsourced visual classifications of color composite image. Images in GZH are selected from various \textit{Hubble Space Telescope} Legacy programs using the Advanced Camera for Surveys (AEGIS, COSMOS, GEMS, GOODS-N, and GOODS-S), with filters selected to probe the rest-frame optical emission from galaxies out to $z\simeq1$. The galaxies selected for GZH classifications go down to magnitude limits of $m_{I814W}<23.5$ and have a median redshift of $\langle z\rangle=0.9\pm0.6$, with a tail extending out to $z\simeq4$. The GZH morphological data includes measurements of both bulge- and disk-dominated galaxies, details on spiral disk structure that relate to the Hubble type, and numerous measurements of clump identification and geometry. This paper also describes and employs a novel method for calibrating morphologies for galaxies of different luminosities and at different redshifts by using artificially-redshifted galaxy images as a baseline. The GZH catalog includes both the raw and calibrated morphological vote fractions for $150,771$ galaxies, providing a comprehensive data set suitable for large-scale studies of galaxy evolution.

\end{abstract}

@@

The morphology of galaxies encodes information on the orbital parameters and assembly history of the contents, including gas, dust, stars, and the central black hole. The morphology is also closely related to the local environment of the galaxy, as mutual interactions such as tides, shocks in cluster environments and direct mergers can all change the shape of the galaxy's gravitational potential. For $M^\star$~galaxies in the local Universe, this typically manifests at the most basic level as the difference between bulge-dominated, virialized systems resembling ellipticals (early-types) and disk-dominated, rotationally-supported disks (late-types) frequently exhibiting spiral arms. This dichotomy has been used to explore much of the astrophysics governing galaxy formation and evolution, and has been shown to be closely linked with other galactic properties such as stellar mass, halo mass, bolometric luminosity, black hole activity, effective radius, and the relative ages of the stellar populations.

The advent of larger telescopes in an increasing range of observing wavelengths has revealed that the distribution and properties of galaxy morphology have strongly evolved over the lifetime of the Universe. At redshift $z\simeq1$ (roughly 6~Gyr after the Big Bang), many galaxies are still in the process of assembling the baryonic mass required to reproduce the structures seen in the present day. This occurs in a variety of pathways, including accretion of baryons from large-scale galactic filaments onto halos via streaming, mergers of individual dark matter halos along with their baryons, conversion of gas into stars via gravitational collapse and star formation, etc. The process can also be slowed or even reversed via feedback from stellar winds, supernovae, and active black holes. Each of these processes affects the galaxy morphology in different ways, and so an accurate measurement of the demographics as a function of redshift provides an extremely powerful observational constraint on the physics involved \citep[for a recent review see][]{con14}.

Theoretical predictions for the morphology of galaxies as a function of redshift are primarily computed within the $\Lambda$CDM cosmological framework. Full treatments of this model gravitational interactions between baryons and dark matter, hydrodynamics of the gas, and baryonic physics related to star formation and evolution. The most advanced simulations now include volumes up to $\sim100$~Mpc$^3$ while simultaneously resolving the smaller scales necessary to reproduce the baryonic physics \citep{vog14a,sch15}. Such simulations predict clustering of galaxies on large scales in a hierarchical assembly model \citep{sil12}. The structure of individual galaxies is affected by the merger history \citep{too72,hop10}, local environment \citep[such as the morphology-density relation;][]{dre80}, initial dark halo mass, and many other factors. Morphologies of individual simulated high-mass galaxies at $z\sim2-3$ commonly show kpc-scale ``clumpy'' structures and few galaxies that are either smooth or well-ordered spirals; asymmetric profiles with strong density contrasts dominate populations in the early Universe until at least $z\sim1$ \citep{gen14}.

Observational studies of galaxies at high-redshift also display a wide range of morphological types, many of which are rare or absent at $z\sim0$. These include spheroids and disks (akin to the ellipticals and spirals seen in the local Universe), but also a significant population of massive, more irregular galaxies, including mergers, tadpoles, chains, double-clumps, and clump-clusters \citep{elm05,elm07,cam11a,for11a,kar15}. In contrast, while grand-design spirals have been observed as far back as $z=2.18$ \citep{law12}, their spatial density suggests that they are exceedingly rare at these higher redshifts, with a very low overall disk fraction \citep{mor13}. Current observational data thus strongly suggests that the classical Hubble sequence/tuning fork \citep{hub36} is not a suitable framework for characterizing high-redshift morphology.

Space-based observatories, particularly the \hubble, have been responsible for the bulk of imaging studies of high-redshift galaxies. Observations of fixed fields with very deep imaging \citep[eg,][]{wil96,gia04,bec06,dav07,sco07,gro11} give the photometric sensitivity necessary to detect $L^\star$ galaxies at $z>1$, while also providing the angular resolution to distinguish internal structure and characterize the morphology. While these measurements are helped by the fact that the angular diameter distance is relatively flat beyond $z>1$ in a flat $\Lambda$CDM cosmology, the relevant angular scales are only of the order $\sim5-10~\mathrm{kpc}/^{\prime\prime}$ \citep{wri06}. \hst{} can thus resolve much of the structure for a Milky Way-sized galaxy out to moderately high redshifts (at least distinguishing a disk from a bulge), but will be limited for more compact structures. Since the size of galaxies evolves as roughly $r\propto(1+z)^{-1}$ \citep{law12a}, the compact sizes of high-redshift galaxies make detailed morphologies a challenge even for \hst{} \citep{che12}. The public availability of more than $10^5$~galaxies in archival imaging across various studies gives a data sample with the potential for high statistical significance.

One of the major difficulties in studying the morphologies of galaxies lies in the techniques used for measurement. Visual classification by experts has been used for many years \citep[eg,][]{hub26,dev59,san61,van76,nai10,bai11,kar15}. These methods have the advantage of using the significant processing power of the human brain to identify patterns, but suffer from issues such as lack of scaling to large surveys and potential issues with replicability and calibration. Automated measurements, both parametric \citep{pen02a,sim11,lac12} and non-parametric \citep{abr03,con03,lot04,sca07,bam08,fre13}, scale well to very large sample sizes, but do not always fully capture the relevant features, especially for asymmetric galaxies that become increasingly common at high redshifts. The Galaxy Zoo project \citep{lin08,lin11} utilizes crowdsourced visual classifications to measure galaxies in color-composite images. The efforts of more than $2\times10^5$~classifiers allow for multiple independent classifications of each image which are combined and calibrated to give a distribution of vote fractions proportional to the probability of a feature being visible. While crowdsourced data require extensive calibration \citep{bam09,wil13}, they have a proven reliability and have been used in dozens of papers \citep[eg,][]{lan08,bam09,dar10,mas11c,ski12,sim13,sch14,wil15}.

This paper presents the results from the Galaxy Zoo Hubble (GZH) project.\footnote{\url{http://zoo3.galaxyzoo.org/}} GZH was the third phase of Galaxy Zoo, following its initial results classifying $\sim900,000$~SDSS~images into primarily early/late~types \citep{lin11} and Galaxy~Zoo~2, which covered $\sim250,000$~SDSS~images using a more detailed classification scheme that included bars, spiral arms, and galactic bulges \citep{wil13}. GZH used a similarly detailed classification scheme, but focused for the first time on images of high-redshift galaxies taken with the \hubble. The Galaxy Zoo: CANDELS project has also classified morphologies of galaxies at high redshift using ACS and WFC3 imaging (Simmons et~al., submitted).

@@

This paper uses the WMAP9 cosmology parameters of $(\Omega_m,\Omega_\Lambda,h)=(0.258,0.718,0.697)$ \citep{hin13}.

%\begin{enumerate}
%    \item Motivation for studying morphology of galaxies
%    \item Particular scientific questions governed by galaxies at $z\sim1$
%    \item Theoretical predictions for galaxy morphology evolution
%    \item Past imaging and morphology studies at $z\sim1$
%    \item Summary of GZ/citizen science work on galaxy morphology to date
%    \item Outline of paper
%\end{enumerate}

@@

The GZH project contains images drawn from a number of different dedicated surveys and sample selection criteria. The majority of the data (as implied by the project name) are taken directly from \hst{} Legacy Surveys, all of which primarily use imaging from the Advanced Camera for Surveys (ACS). Results from the individual surveys have been combined into a single photometric and morphological database, the Advanced Camera for Surveys General Catalog \citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in Table~\ref{tbl:gzh_numbers}.

\begin{figure*}
\center
\includegraphics[width=160mm]{figures/filter_curves.pdf}
\caption{Transmission curves of the filters used by \hst{} Advanced Camera for Surveys (ACS) in wide-field channel mode for the various surveys in GZH. The unfilled black curves show the filters for the Suprime Camera on the \textit{Subaru} telescope, which was used to create color gradients in the GZH images for COSMOS.\label{fig:filtercurves}}
\end{figure*}

\begin{itemize}
\item The All-Wavelength Extended Groth Strip International Survey \citep[AEGIS;][]{dav07} covers a strip centered at $\alpha=14^\textrm{h}17^\textrm{m}, \delta=+52^\circ30^\prime$. This area was selected for a deep survey due to a combination of low extinction and low Galactic/zodiacal emission. The ACS images covered 63 separate tiles over a total area of $\sim710$~arcmin$^2$. The two ACS bands for AEGIS had exposure times of 2300~seconds in F606W (\Vband) and 2100~seconds in F814W (\Iband). The final mosaic images are dithered to a resolution of 0.03~\arcsec/pixel. For extended objects, the limiting magnitudes of sources in AEGIS are 26.23~(AB) in \Vband{} and 25.61 (AB) in \Iband.

\item The Great Observatories Origins Deep Survey \citep[GOODS;][]{gia04} covers two separate fields in the northern and southern hemispheres: the Hubble Deep Field-North ($\alpha=12^\textrm{h}36^\textrm{m}, \delta=+62^\circ14^\prime$) and the Chandra Deep Field-South ($\alpha=03^\textrm{h}32^\textrm{m}, \delta=-27^\circ48^\prime$). The \hst{} ACS imaging data from the two fields are referred to as GOODS-N and GOODS-S, respectively. ACS imaging in GOODS fields used 4 filters -- F435W (\Bband), \Vband, F775W (\iband), and F850LP (\zband). The mean exposure times for each epoch vary by band, from 1050--2100~seconds. The \Bband{} images were completed in a single epoch at the beginning of the survey, but the \Vband, \iband, and \zband{} images were taken in five separate epochs separated by 40--50~days each. Images are dithered to a pixel scale of 0.03~\arcsec/pixel and cover a total area of $\sim320$~arcmin$^2$ (160~arcmin$^2$ per north/south field). The $5\sigma$ limiting magnitudes for extended sources are 25.7 for \Vband{} and 25.0 for \iband.

\item The Cosmic Evolution Survey \citep[COSMOS;][]{sco07} covers an area of $\sim1.8$~deg$^2$ centered at $\alpha=10^\textrm{h}00^\textrm{m}, \delta=+02^\circ12^\prime$. Its location near the celestial equator was designed to enable coverage by ground-based telescopes in both the Northern and Southern Hemispheres, in addition to space-based observatories. The ACS data for COSMOS consists of 1 orbit per pointing with an exposure time of 2028~seconds in \Iband; 590 total pointings are used to cover the entire field. The image resolution is dithered to 0.05~\arcsec/pixel. The 50\% completeness magnitude for a galaxy with a half-light radius of $0.50^{\prime\prime}$ in \Iband{} is 24.7 mag.

\item The Galaxy Evolution from Morphologies and SEDs \citep[GEMS;][]{rix04,cal08} survey is also centered on the Chandra Deep Field-South. The GEMS data covers $\sim800$~arcmin$^2$, completely surrounding the area covered by GOODS-S. Images from ACS in GEMS have 1 orbit per pointing for a total of 63~pointings. The exposure times are 2160 and 2286~seconds in \Vband{} and \zband{}, respectively. The image resolution has a pixel scale of 0.03~\arcsec/pixel. The $5\sigma$ limiting magnitudes for source detection are 25.7 AB in \Vband{} and 24.2~AB in \zband. 
\end{itemize}

@@

In the ACS-GC \citep{gri12}, individual galaxies are identified using a combination of \sextractor{} \citep{ber96} and the \sersic{}-profile fitting framework \galapagos{} \citep{bar12}. GZH includes all galaxies with $m < 23.5$, where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS + GOODS-S, and GOODS-N surveys, respectively. This yielded a total of 113,166~images (Table~\ref{tbl:gzh_numbers}).

Single-epoch images from SDSS Stripe~82 were selected using the same criteria from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ > 3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the $r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The images used are three-color composites using the $g^\prime$, $r^\prime$, and $i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria. Co-added images from Stripe~82 were selected from the union of galaxies with co-added magnitudes brighter than $17.77$~mag and the galaxies detected in the single-depth images and matched to a co-add source. This resulted in a larger set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent) are dimmer than the initial magnitude cut of 17.77.

@@

The images used for classification in GZH are color-composite JPGs made from multi-band data. The exact process for creating the images depends on the bands and resolutions in the surveys.

For galaxies in the ACS-GC, color composites are made using a fixed pixel intensity scaling with weights of $[2.4\times10^{-4},3\times10^{-4},3\times10^{-4}]$ in the red, green, and blue channels respectively. A nonlinear mapping is applied to each pixel to emphasize the contrast in faint features \citep{lup04}, taking the form of:

\begin{equation}
I_\mathrm{channel,new} = I_\mathrm{channel,old} \times \frac{\arcsinh(b\times r)}{(b\times r)}
\label{eqn:nonlinear}
\end{equation}

\noindent The GZH images from \citet{gri12} use a value of $b=3$.

The majority of the data in Legacy surveys described in Section~\ref{ssec:legacy_surveys} had images in only one or two filters available when the GZH project was first launched, making standard 3-channel RGB images in the same method used for the SDSS images in the original Galaxy Zoo impossible. For surveys with images in two bands (AEGIS, GEMS, and the two-epoch GOODS-N and GOODS-S), the lower-wavelength band was mapped to the blue channel, the higher-wavelength band to the red channel, and the green channel created by taking the geometric mean of the two. Bands used in each of the surveys are listed in Table~\ref{tbl:gzh_numbers}. The 2-epoch GOODS-N and GOODS-S images use different filters --- this was a deliberate choice made so that the GEMS images could be directly compared with the overlapping coverage of GOODS-S (Figure~\ref{fig:filtercurves}).

By the time that the 5-epoch sets of GOODS data were put into GZH (in March 2015), coverage in four separate \hst{} bands were publicly available. The deeper GOODS images were created using the arithmetic mean of \Bband{} and \Vband{} in the blue channel, \Iband{} in the red channel, and \zband{} in the green channel. These images also had their speckled noise pixels decolorized.

The COSMOS images only had the \Iband{} imaging available at the time of classification in GZH. For these galaxies, we created ``pseudocolor'' images by using the ACS \Iband{} data as the illumination map and ground-based imaging from the \subaru{} telescope in $B_J$, $r^+$, and $i^+$ filters to provide the color gradients \citep[see][for further details]{gri12}. This means that the images have the angular resolution of \hst{} ($\sim0.05$~\arcsec/pixel) for the overall intensity, but the color gradients are at ground-based resolution, with seeing between 0.95\arcsec{} and 1.05\arcsec{} \citep{tan07}.

Stripe~82 single-epoch images were taken directly from the color composites on the DR7 SDSS Skyserver, which combines $g^{\prime}$, $r^{\prime}$, and $i^{\prime}$ exposures into the RGB channels. The co-added Stripe~82 images were assembled from runs 106 and 206 in DR7 and made into color composites using the method of \citet{lup04}, as in previous iterations of Galaxy Zoo.

To deal with images in which the sky noise was highly colored (which might have been a distraction to visual classification), a soft-edged object mask was applied that preserves the color balance for galaxies, but desaturates speckled noise against regions of blank sky. This technique was applied only to the co-added Stripe~82 and the COSMOS images.

@@

GZH also includes a set of images designed to measure the effect of active galactic nuclei (AGN) on morphological classifications. Since galactic nuclei can have bright, unresolved optical emission, this has the potential to mimic or distort the identification of a bulge component. The presence of an AGN is simulated by modeling the point spread function (PSF) of the telescope and then inserting a bright source near the center of a real galaxy. For each image, the simulated AGN is assigned one of three colors -- either blue, red, or flat (white) as seen in the color images -- and a range of brightnesses such that $L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in $(0.2,1.0,2.0,5.0,10.0,50.0)$. This range was selected to run from AGN which were all but undetectable through to those which dominate the galaxy, providing coverage of all plausible effects. Combining these parameters generates 15~images with different simulated AGN for each host.

Two sets of simulated AGN were generated in GZH. The first set (version~1) was assembled from 95~galaxies from GEMS imaging and PSFs from \texttt{daophot}. The second set (version~2) was assembled from 96~galaxies in GOODS-S; this version used deeper imaging and improved PSFs from \texttt{TinyTim}.

Images with simulated AGN were classified in the main interface in an identical manner and evenly distributed with unaltered images of the galaxies. Classifiers were not explicitly told that the images had been altered, as the goal was to measure the effect on normal classifications in as unbiased a manner as possible.
